### 2023-07-31 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
worked on last couple figures and contracting section

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\label{subsec:Contraction} A multicomponent vesicle in the
contracting geometry}
In this section, we consider a single vesicle passing through a geometry
that slowly contracts to a region that is only 2~$\mu$m wide, and then
immediately opens back up to a channel that is ten times larger. We
first consider the effect of the initial lipid concentration when the
floppy and stiff regions each make up half of the vesicle membrane. In
Figure~\ref{fig:RA6leftRightRand}, we consider a vesicle with $\alpha =
0.6$ with an initially random initial lipid concentration, one that is
floppy in the front and stiff in the back, and one that is stiff in the
front and floppy in the back. The vesicle with the random initial lipid
distribution quickly phase separates into a two floppy and two stiff
regions. As seen in the stenosis geometry, further phase separation is
delayed until the vesicle is no longer under strong confinement. The
vesicle where the initial lipid species distribution is fully phase
separated with the floppy region on the front of the vesicle begins to
reorient the floppy region to the back of the vesicle. In contrast, the
fully phase separated case with the stiff region at the front maintains
its orientation. In summary, in all three cases, the vesicle is
orienting itself so that the stiff region passes through the
constriction before the floppy region. Therefore, in all subsequent
examples, we start with symmetric vesicle whose floppy region is in the
back and its stiff region is in the front. The vesicle shapes develop
regions with high curvature in the floppy region when they first pass
through the narrowest part of the geometry, but because the strong
confinement is abruptly removed immediately afterwards, these regions of
high curvature are quickly smoothed. 
%Since we can see in Figure~\ref{fig:RA6leftRightRand} that the regions
%of high curvature are located in the back of the vesicle, we expect the
%overall bending energies to be lowest for the randomly distributed case
%and the fully separated floppy region on the back case. We observe this
%in Figure~\ref{fig:RAp6leftRightRandBending}.

\begin{figure}[H]
  \centering
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 2cm .5cm},clip]{(a)}{figures/rightSep.pdf}
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 2cm .5cm},clip]{(b)}{figures/randSep.pdf}
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 2cm .5cm},clip]{(c)}{figures/leftSep.pdf}
  \includegraphics[width=\columnwidth]{figures/Contracting_RAp6MCp5.pdf}
  \caption{\label{fig:RA6leftRightRand} \small A multicomponent vesicle
  with 50\% floppy region passing through a contracting geometry. The
  vesicle's reduced area is $\alpha = 0.6$ and the capillary number is
  $Ca = 0.25$. The lipid distribution is initialized to already be phase
  separated in the top and bottom rows, and the middle row has a random
  initial lipid distribution. The preferred orientation of the lipid
  concentration is to have the stiff region to pass through the
  contraction before the floppy region.}
\end{figure}

@@

In addition to the lipid distribution, the percentage of the vesicle
that is floppy plays a role in the vesicle dynamics. Therefore, we
consider a vesicle with reduced area $\alpha = 0.5$ in a contracting
geometry with various sizes of the floppy region. Motivated by the last
experiment, we initialize the lipid distribution so that the front is
stiff and the back is floppy. In each simulation, the capillary number
is $Ca = 0.25$. Figure~\ref{fig:RA5} shows the vesicle shapes as they
pass through the narrow constriction when the percentage of the floppy
region is 0\% (single-component), \%15, \%25, \%35, and \%45. One effect
of the size of the floppy region is that the symmetry of the vesicle
shape is broken at smaller percentages. We also see that stiffer
vesicles have faster migration speeds, but the effect is quite small. In
Table~\ref{tbl:contractingTimes}, we report the time the vesicle first
passes through the neck.
%In Figure~\ref{fig:RA5}, we consider a vesicle with reduced area
%$\alpha = 0.5$ and the capillary number is $Ca = 0.25$. We start with a
%single-component vesicle and then increase the percentage of the
%vesicle membrane that is floppy. By comparing the vesicle location at
%the time step just before the vesicle passes through the constriction,
%we can immediately see that vesicles with membranes that have larger
%percentage of floppy regions reach and pass through the neck earlier.
%The dimensionless times that the entire vesicle first passes through
%the neck are reported in Table~\ref{tbl:contractingTimes}.

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=\columnwidth]{figures/bendingAllContracting.pdf}
  \caption{\label{fig:bendingAll} \small The bending energy for a
  single-component vesicle (blue) and a multicomponent vesicle
  (red)--(green) with $\alpha = 0.5$. As the size of the floppy region
  increases, the maximum bending energy decreases.}
\end{figure}

\todo[inline]{Bryan is here}
We conclude this example by considering the different shapes that
single-component and multicomponent shapes display. Since we have
initialized the lipid species to initially be phase separated, the phase
energy is more or less constant for all cases. The tension energy, on
the other hand, increases as the vesicle approaches the neck, but its
general shape is similar for the five cases considered in
Figure~\ref{fig:RA5}. However, the bending energies are show different
behaviors for each of the cases (Figure~\ref{fig:bendingAll}). The main
difference between the cases is the that multicomponent vesicles with a
higher percentage of floppy regions have less bending energy, especially
as the vesicle passes through the neck. We also note that the bending
energy undergoes several transient increases and decreases. These occur
when the tail of the vesicle undergoes transitions from lower energy
shapes, such as a `C' or `S' shapes, to high energy shapes, such as 'W'
shapes. Figure~\ref{fig:bendingSC_contracting} show these different
vesicle shapes for the single-component vesicle and multicomponent
vesicle that is 45\% floppy. The shape at several critical points along
the bending energy are included, and we can indeed see that
transitioning vesicle shape between these different states.

\begin{figure}
    \centering
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(a)}{figures/Fig14f.pdf}
    \subfigimg[width=\columnwidth]{(a)}{figures/bendingSC.pdf}
    \subfigimg[width=\columnwidth]{(b)}{figures/bendingEngMC45.pdf}
    \caption{\label{fig:bendingSC_contracting} The bending energy of (a) a single-component vesicle, and (b) a multicomponent vesicle whose boundary is 45\% floppy passing through a contracting geometry. The vesicle shape at different locations are included. We can clearly see that the sudden increases and decreases in the bending energy are due to transitions between lower energy and higher energy shapes.}
\end{figure}

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\label{subsec:Contraction} A multicomponent vesicle in the
contracting geometry}
In this section, we consider a single vesicle passing through a geometry
that slowly contracts to a region that is only 2~$\mu$m wide, and then
immediately opens back up to a channel that is ten times larger. We
first consider the effect of the initial lipid concentration when the
floppy and stiff regions each make up half of the vesicle membrane. In
Figure~\ref{fig:RA6leftRightRand}, snapshots of vesicles with reduced
area $\alpha = 0.6$ with different initial lipid distributions are
illustrated. The initial distributions are random (middle) floppy in the
front and stiff in the back (top), and one that is stiff in the front
and floppy in the back (bottom). The vesicle with the random initial
lipid distribution quickly phase separates into two floppy and two stiff
regions. As seen in the stenosis geometry, further phase separation is
delayed until the vesicle is no longer under strong confinement. The
vesicle with the floppy region on the front reorients the floppy region
towards the back of the vesicle. In contrast, the vesicle with the stiff
region at the front maintains its orientation. In summary, in all three
cases, the vesicle is orienting itself so that the stiff region passes
through the constriction before the floppy region.  Therefore, in
subsequent simulations, we initialize the vesicle's lipid concentration
so that the floppy region is in the back and its stiff region is in the
front. The vesicle shapes develop regions with high curvature in the
floppy region when they first pass through the narrowest part of the
geometry, but because the strong confinement is abruptly removed
immediately afterwards, these regions of high curvature are quickly
smoothed. 
%Since we can see in Figure~\ref{fig:RA6leftRightRand} that the regions
%of high curvature are located in the back of the vesicle, we expect the
%overall bending energies to be lowest for the randomly distributed case
%and the fully separated floppy region on the back case. We observe this
%in Figure~\ref{fig:RAp6leftRightRandBending}.

\begin{figure}[H]
  \centering
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 2cm .5cm},clip]{(a)}{figures/rightSep.pdf}
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 2cm .5cm},clip]{(b)}{figures/randSep.pdf}
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 2cm .5cm},clip]{(c)}{figures/leftSep.pdf}
  \includegraphics[width=\columnwidth]{figures/Contracting_RAp6MCp5.pdf}
  \caption{\label{fig:RA6leftRightRand} \small A multicomponent vesicle
  with 50\% floppy region passing through a contracting geometry. The
  vesicle's reduced area is $\alpha = 0.6$ and the capillary number is
  $Ca = 0.25$. The lipid distribution is initialized to already be phase
  separated in the top and bottom rows, and the middle row has a random
  initial lipid distribution. The preferred lipid distribution has the
  stiff region passing through the contraction before the floppy
  region.}
\end{figure}

@@

In addition to the lipid distribution, the percentage of the vesicle
that is floppy plays a role in the vesicle shapes and dynamics.
Therefore, we consider a vesicle with reduced area $\alpha = 0.5$ in the
contracting geometry with various sizes of the floppy region. Motivated
by the last experiment, we initialize the stiff region to be in the
front and the floppy region to be in the back. In each simulation, the
capillary number is $Ca = 0.25$. Figure~\ref{fig:RA5} shows the vesicle
shapes at the same six time steps when the percentage of the floppy
region is 0\% (single-component), \%15, \%25, \%35, and \%45. One effect
of the size of the floppy region is that the symmetry of the vesicle
shape is broken at smaller percentages. We also see that stiffer
vesicles have faster migration speeds, but the effect is quite
small---Table~\ref{tbl:contractingTimes} reports the time the vesicle
first passes through the neck.
%In Figure~\ref{fig:RA5}, we consider a vesicle with reduced area
%$\alpha = 0.5$ and the capillary number is $Ca = 0.25$. We start with a
%single-component vesicle and then increase the percentage of the
%vesicle membrane that is floppy. By comparing the vesicle location at
%the time step just before the vesicle passes through the constriction,
%we can immediately see that vesicles with membranes that have larger
%percentage of floppy regions reach and pass through the neck earlier.
%The dimensionless times that the entire vesicle first passes through
%the neck are reported in Table~\ref{tbl:contractingTimes}.

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=\columnwidth]{figures/bendingContracting.pdf}
%  \includegraphics[width=\columnwidth]{figures/bendingAllContracting.pdf}
  \caption{\label{fig:bendingAll} \small The bending energy for a
  single-component vesicle (blue) and a multicomponent vesicle
  (red)--(green) with $\alpha = 0.5$. As the size of the floppy region
  increases, the maximum bending energy decreases.}
\end{figure}

\todo[inline]{Bryan is here}
We conclude this example by considering the different shapes that
single-component and multicomponent shapes display. Since we have
initialized the lipid species to initially be phase separated, the phase
energy is nearly constant for all cases, and is therefore not plotted.
The tension energy, on the other hand, increases as the vesicle
approaches the neck, but its general shape is similar for all five
cases, and it too is not plotted. However, the bending energies show
different behaviors for each of the cases (Figure~\ref{fig:bendingAll}).
The main difference being that the multicomponent vesicles with a higher
percentage of floppy regions have less bending energy, especially as the
vesicle passes through the neck. We also note that the bending energy
undergoes several transient increases and decreases. These occur when
the tail of the vesicle undergoes transitions from lower energy shapes,
such as `C' or `S' shapes, to high energy shapes, such as 'W' shapes.
Figure~\ref{fig:bendingSC_contracting} shows these different vesicle
shapes for the single-component vesicle and multicomponent vesicle that
is 45\% floppy. The shapes at several critical points along the bending
energy are included, and we can indeed see that transitioning vesicle
shape between these different states.

\begin{figure}
  \centering
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(a)}{figures/Fig14f.pdf}
  \subfigimg[width=\columnwidth]{(a)}{figures/ContractingEnergy_SC.pdf}
  \subfigimg[width=\columnwidth]{(b)}{figures/ContractingEnergy_MC.pdf}
%  \subfigimg[width=\columnwidth]{(a)}{figures/bendingSC.pdf}
%  \subfigimg[width=\columnwidth]{(b)}{figures/bendingEngMC45.pdf}
  \caption{\label{fig:bendingSC_contracting} The bending energy of (a) a
  single-component vesicle, and (b) a multicomponent vesicle whose
  boundary is 45\% floppy passing through a contracting geometry. The
  vesicle shape at different locations are included. We can clearly see
  that the sudden increases and decreases in the bending energy are due
  to transitions between lower energy and higher energy shapes.}
\end{figure}

@@

\begin{itemize}
  \item New bending model using hyperbolic tangent (sigmoidal shape)
    which is necessary to maintain a positive bending modulus

  \item Orientation of the phase is always stiff on the front and floppy
    on the back, but we don't know why (yet). Observed by others such as
    Biros and Agrawalla, George and Misbah, and others.

  \item Boundary layer and change in sign of pressure gradient term that
    drives the lubrication flow. This is a combination of the tension
    and the phase boundary between stiff and floppy regions.

  \item Sudden drop in bending energy for multicomponent can be
    explained by the sudden coarsening of the lipids.

  \item Relationship between tank treading, excess pressure and layer
    thickness.

  \item  Inability to coarsen when under strong confinement. Can be
    related to item 2. Strong confinement arrests phase coarsening.

\end{itemize}
